The problem and promise of scale in multilayer networks

### 2020-01-23 paper/manuscript.Rmd
edit fitness P3

Social network structure depends on the timeframe of observation, which can make networks difficult to compare (Castles et al., 2014). Furthermore, social network structure can vary seasonally and indicate social environments that an individual experiences (e.g. Brent, MacLarnon, Platt, & Semple, 2013; Hamede, Bashford, McCallum, & Jones, 2009; Holekamp, Smith, Strelioff, Van Horn, & Watts, 2012), or they can be consistent across time, which can be used to reflect social phenotypes (Aplin et al., 2015; Stanley, Mettke-Hofmann, Hager, & Shultz, 2018). Seasonal fluctuations have the potential to have disease transmission and fitness effects for individuals (Balasubramaniam et al., 2019; Chen et al., 2014).

Additionally, in long-lived species especially, social network metrics of individuals can change over their lifetimes in ways that can have impacts on their reproductive success and longevity (Berger et al., 2015; Brent et al., 2017). These findings highlight the necessity to think carefully about the temporal scale that is meaningful for the proposed hypotheses, especially for understanding individual social phenotypes or environments and how they relate to that individual’s fitness. Further complicating the issue, social network metrics can change over stages of ontogeny, but individuals progress through development at different rates (Tarka, Guenther, Niemelä, Nakagawa, & Noble, 2018). This variation can make defining appropriate temporal scales for testing the fitness implications of an individual’s social network position over different stages of ontogeny even more difficult. However, thinking about temporal scales at such a fine level can provide insights for important stages of development that may have otherwise been missed (CITE-myself??). However, multilayer networks provide a framework to test hypotheses about how social dynamics over time relate to fitness. Because of the non-independent nature of social interactions, especially over time, it is hard to test hypotheses about social dynamics with a suitable null control (Farine, 2017; Proskurnikov & Tempo, 2017). Using the framework of multilayer networks, making layers of different temporal periods provides a way to make appropriate null models to test questions about the dynamics of an individual’s social network position over multiple aggregated time periods.

>>>>

Social network structure depends on the timeframe of observation, which can make networks difficult to compare (Castles et al., 2014). Furthermore, social network structure can vary seasonally and indicate social environments that an individual experiences (e.g. Brent, MacLarnon, Platt, & Semple, 2013; Hamede, Bashford, McCallum, & Jones, 2009; Holekamp, Smith, Strelioff, Van Horn, & Watts, 2012), or they can be consistent across time, which can be used to reflect social phenotypes (Aplin et al., 2015; Stanley, Mettke-Hofmann, Hager, & Shultz, 2018). Seasonal fluctuations have the potential to have disease transmission and fitness effects for individuals (Balasubramaniam et al., 2019; Chen et al., 2014). **[QW: I'm not sure what this paragraph adds - I think if we need to save space we could cut it]**

In long-lived species, social phenotypes can change over their lifetimes in ways that can have affect fitness (Berger et al., 2015; Brent et al., 2017). These findings highlight the necessity to carefully consider the temporal scale that is meaningful for the proposed hypotheses, especially for understanding the relationship between an individuals social phenotypes and fitness. Further complicating the issue, social phenotypes can change over stages of ontogeny, although it is important to note that individuals progress through development at different rates (Tarka, Guenther, Niemelä, Nakagawa, & Noble, 2018). This variation can make defining appropriate temporal scales for testing the fitness implications of an individual’s social phenotype over different stages of ontogeny even more difficult. However, considering fine temporal scales may provide insight across development stages that may otherwise be missed (CITE-myself??). Multilayer networks provide a framework to test hypotheses linking social phenotypes and fitness across temporal scales. Because of the non-independent nature of social interactions and associations, especially over time, it is hard to test hypotheses about social dynamics with a suitable null control (Farine, 2017; Proskurnikov & Tempo, 2017). Using the framework of multilayer networks, making layers of different temporal periods provides a way to make appropriate null models to test questions about the dynamics of an individual’s social network position over multiple aggregated time periods.
